|

### 2022-07-24 manuscript.Rmd
add some citations

```{r pkg, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, purl=FALSE}
# Load required packages
## Any packages loaded in this chunk will automatically be added to `bib/packages.bib` for citation use
library(ggplot2)
library(scales)
library(BrailleR)
library(sonify)
library(tactileR)
library(tidyverse)
```

@@

Although there are various ways to represent data patterns and models, visualization has been primarily taught in many data science courses for its efficiency (cite). 
Such vision-dependent output may cause critical barriers against those who are blind and visually impaired, and sometimes people with learning disabilities. 
We argue that instructors need to teach multiple data representation methods so that all students of all abilities can benefit from multi-sensory data augmentation.

@@

Once alt text is prepared either programmatically or manually, it can be embedded in static and dynamic plot objects in R, such as `ggplot2::labs(..., alt = "[alt text]")`, 
`shiny::renderPlot(..., alt = "[alt tex]")`. 
We also ask our students to provide alt text within their R Markdown chunks by using `fig.alt = "[alt text]"` chunk option, and within Pandoc-flavor/Common Markdown with `![alt text here.](path/to/file)` syntax.

>>>>

```{r pkg, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, purl=FALSE}
# Load required packages
## Any packages loaded in this chunk will automatically be added to `bib/packages.bib` for citation use
library(ggplot2)
library(scales)
library(BrailleR)
library(sonify)
library(tactileR)
library(tidyverse)
library(shiny)
library(knitr)
```

@@

Although there are various ways to represent data patterns and models, visualization has been primarily taught in many data science courses for its efficiency [@kimAccessibleVisualizationDesign2021]. 
Such vision-dependent output may cause critical barriers against those who are blind and visually impaired, and sometimes people with learning disabilities [@kimAccessibleVisualizationDesign2021; @marriottInclusiveDataVisualization2021; @leeReachingBroaderAudiences2020]. 
We argue that instructors need to teach multiple data representation methods so that all students of all abilities can benefit from multi-sensory data augmentation.

@@

Once alt text is prepared either programmatically or manually, it can be embedded in static and dynamic plot objects in R, such as `ggplot2::labs(..., alt = "[alt text]")`, 
`shiny::renderPlot(..., alt = "[alt tex]")` [@R-shiny]. We also ask our students to provide alt text within their R Markdown chunks by using `fig.alt = "[alt text]"` `knitr` chunk option [@knitr2014], and within Pandoc-flavor/Common Markdown with `![alt text here.](path/to/file)` syntax [@macfarlanePandoc2022].
